Investigating the applications and limits of single particle light scattering using limited detection schemes

### 2022-11-02 Investigation into low light scattering.tex
Add files via upload

	Where $p(\hat{n})$ and $p(y)$ are our estimations of the priori distributions of particle orientations and scattering signals respectively. The former can be estimated by some Boltzmann distribution based on the radial distance between neighbouring reference orientations. This essentially is biasing our estimate by tying it to its proximity in the orientation space. The latter priori can be taken as the integral of  $p(y(\hat{s})\parallel \hat{n})$ and $p(\hat{n})$ across all possible reference orientations. In order to evaluate if our model is accurate we need first test it using an idealised simulation of the target dimer.

@@

	Since we are testing with a simulation we already know the exact orientation of the dimer, we want to know if our model can correctly predict the closest reference orientation. We take the dot product between our estimated $\hat{n}$ and the correct $\hat{n}$ and calculate the angle between the two. Performing a summation over the full simulation data we should see that the model has a total

	\begin{align}
		K_l(B \parallel D) &= - \sum_{n=1}^{no. steps} B_n \ln(\frac{D_n}{B_n})
	\end{align}

	Where $B_n$ is the Bayesian estimate and $D_n$ is the dot product result; the closer our estimate is to the dot product result the more accurate the model, and the divergence will approach 0. We can therefore evaluate the overall accuracy of our estimate based on the divergence - which is determined primarily by the detection angles.

@@

	We used the Ultra-nest software to create a set of live points of different choices of detection angles, with each point being evaluated by the divergence ($K_l(B\parallel D)$) produced. After evaluating every live point, the worst results are removed and new live points are created based on the information provided by the previous live points. This results in a convergence on parameter choices that result in an average divergence result of almost 0. A common issue with complex parameter spaces, such as ours, is the issue of degeneracies (where two or more parameters have identical parameter spaces), to combat this we implemented a random step sampler that selects a new live point some 'n' steps away in the parameter space.

>>>>

	Where $p(\hat{n})$ and $p(y)$ are our estimations of the priori distributions of particle orientations and scattering signals respectively. The former can be estimated by some Boltzmann distribution based on the radial distance between neighbouring reference orientations. This essentially is biasing our estimate by tying it to its proximity in the orientation space. The latter priori can be taken as the integral of $p(y(\hat{s})\parallel \hat{n})$ and $p(\hat{n})$ across all possible reference orientations. In order to test the accuracy of our model we first test it using an idealised simulation of the target dimer.

@@

	Since we are testing with a simulation we already know the exact orientation of the dimer, we want to know how often our model can determine the closest reference orientation $\hat{n}$ to the true orientation $\hat{s}$, and how precise our prediction is. For a perfect model our probability distribution should be peaked at the correct result and zero elsewhere.
	\begin{equation}
		p_{ideal}=
		\begin{cases}
			1 & \text{when $\hat{n}$ = $\hat{n}_{best}$}\\
			0 & \text{anywhere else}
		\end{cases}
	\end{equation}

	In reality our model will be some probability distribution that has some probability of any orientation being correct. To evaluate our model's accuracy and confidence we calculate the Kullback-Leibler divergence of the two probability distributions.

	\begin{align}
		K_{l, \#}(p_{guess} \parallel p_{ideal}) &= 
		p(\hat{n}\parallel y_k(\hat{s})) \ln \left[
		\frac{p_{ideal}}{p(\hat{n}\parallel y_k(\hat{s}))}
		\right]
	\end{align}

	Where the divergence goes to zero if $p_{ideal}=0$, for a single estimation this gives us an idea of both the accuracy and the spread of our probability distribution. We sum the divergence of each measurement across the entire simulation to get a score for the entire simulation.

	\begin{align}
		K_{l,total} = \sum\limits_{\# =1}^{no. of steps} K_{l,\#}
	\end{align}

	Since our divergence result is a product of our choice of angles we can see analyse how the choice of angles can be altered to improve our estimate.

@@

	We used the Ultra-nest software to create a set of live points of different choices of detection angles, with each point being evaluated by the divergence ($K_{l, total}$) produced. After evaluating every live point, the worst results are removed and new live points are created based on the information provided by the previous live points. This results in a convergence on parameter choices that result in an average divergence result of almost 0. A common issue with complex parameter spaces, such as ours, is the issue of degeneracies (where two or more parameters have identical parameter spaces), to combat this we implemented a random step sampler that selects a new live point some 'n' steps away in the parameter space.
